\thispagestyle{plain}
\makeatletter
\section*{Acknowledgements}
I guess for all of us the last year was very challenging in every way possible. Despite all the unfortunate circumstances I was lucky enough to be able to complete this important chapter of my life. This would not have been possible if I would not have had the right people around me. 
\begin{itemize}
	\item First and foremost I have to thank my supervisor Prof. Jan Pawlowski for allowing me again to join his amazing group and providing me with such an interesting project. Since the beginning of my Bachelor thesis about two years ago I had the pleasure to enjoy many discussions about physics and beyond with you that contributed greatly to my (not only) scientific knowledge.
	\item I also want to thank Prof. J\"org J\"ackel for agreeing to become the second referee for this thesis in the first place, but I am even more thankful for the time and effort he invested in helping me to find a suitable PhD project.
	\item My deepest gratitude belongs to  Jan Horak, not only for sharing his notes and giving advice concerning calculations and numerics but especially for always finding the time to discuss problems and for keeping me on track during all the ups and downs of the time in home office. It is due to him and his expertise that this project somehow succeeded in the end.
	\item I thank all members of the Strongly Correlated Systems Group for providing such a supportive and welcoming working environment and for all the meetings, game nights and pizza days, that kept the social spirit high during lockdown. I can only imagine how great this year would have been with all of you at the institute!
	\item For valuable comments on the transcript I want to thank  Fabian Glaser and Carl von Randow. Carl deserves an additional honorable mention for his incredible ability to spot even the tiniest code bugs and for his emotional support during many (late night) coding sessions, not only in the scope of this Master thesis. Additionally, I want to thank my dear friends Mercal Abdin and Marie Wintergerst that I can always rely on when it comes to proofreading and whenever I need them.	
	\item At this point I also want to thank Prof. Arthur Hebecker for his excellent lectures on various aspects of theoretical physics I had the pleasure to attend during my studies that built the foundation for developing my fascination for theoretical physics already in the early phases of my studies.
	\item As my studies come to an end I want to take the chance to thank my former high school teachers for arousing my interest in physics and mathematics that ultimately lead to the decision to study physics, a decision I have never regretted. Just to name the most influential ones I want to thank Josef Waltz for being such an inspiring math teacher,  Dr. Christopher B\"uhler who showed me how much fun it is to work on physics problems (even during examinations), Bj\"orn Lennartz for introducing me to many interesting aspects of physics in my last years of school and finally Michael J\"ulich for creating possibilities to discuss interesting topics beyond the scope of my studies, keeping me busy with challenging papers and for the possibility to share my passion for physics with his students for many years now.	
	\item Last but definitely not least, I thank my family and friends for all their support, confidence and time throughout the entire time of my studies. This includes of course my parents Marie-Paule und Bernd and my sister C\'{e}line, Ralf \& Bea, the original \enquote{Nobelpreistr\"ager} crew Alex, Benny, Berkay and Carl, who never failed to motivate and entertain me during lectures, exercise groups, endless exercise sheet sessions and beyond university since the first day of the preparation course and all other friends, no matter whether in Heidelberg or back home, that made the time of my studies so enjoyable.
\end{itemize}
\hfill
\thispagestyle{plain}
\section*{Declaration of Authorship}
I hereby certify that this thesis  has been composed by me and is based on my own work. \\
 Where I have consulted work of others it is always clearly attributed and where I have quoted work from others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.    \\
 
Eppelheim, June 15th 2021 \hfill \rule{60mm}{.15mm} \par \vspace{-0.4em}
\hfill \@author
\vfill
\makeatother 